High-resolution ALMA observations of V4046\,Sgr: a circumbinary disc with a thin ring

### 2021-05-27 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

As mentioned before, the model presented here gives a solution to a highly degenerative problem. Nevertheless, as a way to improve and obtain a rough measure of the accuracy of our model, we made one dimensional explorations of the parameter space and found uncertainties of some relevant parameters that will be useful for the discussion (see Appendix.~\ref{sec:Appendix}). We can estimate that the scale height at $r_\circ$= 18\,au is $H_\circ = 0.92^{+0.01}_{-0.01}$\,au, the width of Ring13 is $w_\mathrm{g} = 5.18^{+0.42}_{-0.16}$\,au for the gas and $w_\mathrm{g} = 2.00^{+0.08}_{-1.4}$\,au, the location of Ring5 is $r=5.2^{+0.05}_{-0.7}$\,au and its width is $w_\mathrm{Ring5} = 0.59^{+0.08}_{-0.36}$\,au.

Given those uncertainties for the width of Ring13 and the , one thought that arise is that the inner ring could be much thinner than our ALMA measurements The intrinsic error of the {\tt uvmem} correction can not be known with high accuracy, so the approximate beam may not be $1/3$ of the beam in natural weights but higher. Any change in this factor would translate to into a narrower Ring13. With a $2/5$ factor, the width of Ring13 is 2.28$\pm$0.51\,au, resulting in a marginally resolve ring. T

@@

The model presented here has many degrees of freedom and each model requires a high level of computational power and time, so a MCMC optimization or similar methods of parameter exploration are impossible to acquire. But as a way to compute a measure of goodness of fit and to try to quantify the improvements we did a partial exploration of the parameter space. Varying the value for one parameter and calculating chi-square for each new value, given $\chi^2_m$ the model chi squared value, the uncertainties (up and down) will be those with $\chi^2=\chi^2_m+1$. Assuming a quadratic behavior for the curve fitting,
\begin{figure*}
	\includegraphics[width=\textwidth]{plot_chi_all.pdf}
        \caption{one dimensional explorations of the chi squared space of our parametric model. {\it Top:} scale height at $r_\circ$=18\,au, width of }
    \label{fig:chi}
\end{figure*}

The

>>>>

As mentioned before, the model presented here gives a solution to a highly degenerative problem. Nevertheless, as a way to improve and obtain a rough measure of the accuracy of our model, we made one dimensional explorations of the parameter space and found uncertainties of some relevant parameters that will be useful for the discussion (see Appendix.~\ref{sec:Appendix}). We can estimate confidence intervals for the scale height at $r_\circ$= 18\,au with $H_\circ = 0.92^{+0.01}_{-0.01}$\,au, for the location of Ring5 with $r=5.2^{+0.14}_{-0.36}$\,au, and for the width of gas Ring13 of $w_\mathrm{g} = 5.18^{+0.33}_{-0.20}$\,au.

%Given those uncertainties for the width of Ring13 and the , one thought that arise is that the inner ring could be much thinner than our ALMA measurements The intrinsic error of the {\tt uvmem} correction can not be known with high accuracy, so the approximate beam may not be $1/3$ of the beam in natural weights but higher. Any change in this factor would translate to into a narrower Ring13. With a $2/5$ factor, the width of Ring13 is 2.28$\pm$0.51\,au, resulting in a marginally resolve ring. T

@@

The model presented here has many degrees of freedom and each model requires a high level of computational power and time, so a MCMC optimization or similar methods of parameter exploration are impossible to acquire. But as a way to compute a measure of goodness of fit and to try to quantify the improvements we did a partial exploration of the parameter space. We explore $\chi^2$ space in the vicinity of the model values for the scale height at $r_\circ$, the location of Ring5, the width of the gas component of Ring13, the width of the gas part of Ring5, the width of the large dust portion of Ring13 and around the lower limit of the grain sizes in the blob. The parameter space exploration is shown in Figure~\ref{fig:chi}. Our model fits the SED and two images, so the total $\chi^2$ value for a given model is composed of the sum of the $\chi^2$ values for each of the three fits.

For the first three parameters, we find that the value of the parameter in our model is almost at a minimum in its one dimensional $\chi^2$ space, so given $\chi^2_m$ the total chi squared value for the model, the uncertainties (up and down) will be those with $\chi^2=\chi^2_m+1$. As the values are around a local minimum, we can as assume a quadratic equation for the curve fitting.

For the the other three parameters, we found that although our chosen values are close to a minimum, the geometries are more suggestive of different border conditions. These exploration allow us to support the idea of Ring5, as it is clear that the absence of it creates a great increment in the total $\chi^2$ value, but also that the ring must be quite thin. For the case of the lower limit of the central blob, it is evident that there is a threshold around 500\,$\micron$, where the SED start to deviate far away from a minimum, that point represent where the NIR excess becomes significant.

\begin{figure*}
	\includegraphics[width=\textwidth]{plot_chi_squared_all800.pdf}
        \caption{one dimensional explorations of the chi squared space of our parametric model. Each panel display at the bottom the $\chi^2$ values for the SED and for the two images separately, and on top the total $\chi^2$ value in terms of the parameter value. {\it Top:} scale height at $r_\circ$=18\,au, location of Ring5, width of the gas component of Ring13. {\it Bottom:} Width of the gas part of Ring5, width of the large dust section of Ring13, lower limit of the grain sizes in the blob.}
    \label{fig:chi}
\end{figure*}
